MLH1 data report 

### 2017-10-12 rmd_report.rmd
playing with permutation code

MLH1_by_F_strain <- MLH1_data[MLH1_data$sex == "female", ]
MLH1_by_M_strain <- MLH1_data[MLH1_data$sex == "male", ]

@@

Currently this section is under construction.

>>>>

MLH1_by_F_strain <- MLH1_data[MLH1_data$sex == "female", ]
MLH1_by_M_strain <- MLH1_data[MLH1_data$sex == "male", ]
```

@@

Currently this section is under construction.
```{r}
# use q_cut_off table, to find the mice to use
listOmice <- q_cutoff_table$mouse[ (q_cutoff_table$total >= 25) ]
#mke new df with from 
df.pasd.mice <- MLH1_data[MLH1_data$mouse %in% listOmice, ]

#write function --- for taking 100 samples of 10

permut.df <- function(df){
  #semperate by mouse
    mouse.data    <- ddply(df, c("mouse"), summarise,
       df <- data.frame(
              samp = sample(nMLH1.foci,5)
            ) 
        )

  return(mouse.data)
}

mouse.data <- ddply(df.pasd.mice, c("mouse"), summarise,

  m.df <- data.frame(sample(nMLH1.foci, 5, replace = FALSE) )
  )

# this creates dataframe, which is a subset of larger dataframe ... not sure se_alone, but samples 40 of 
this =ddply (df.pasd.mice, .(mouse), subset, sample(seq_along(nMLH1.foci)<=5))

ss <- sample(df.pasd.mice$nMLH1.foci)

Table_BD_mouse <- ddply(BDMLH1_data, c("ANIMAL_ID", "Cross"), summarise,
                       N  = length(nMLH1_foci),
                       mean_co = format(round( mean(nMLH1_foci), 3), nsmall = 3),
                       var = format(round( var(nMLH1_foci),3), nsmall = 3),
                       sd   = round(sd(nMLH1_foci),3),
                       se   = round(sd / sqrt(N),3)
                       #text=paste(Cross, collapse=""))
)
